\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-10-23 doc/flexiblesusy-paper.tex
modified a little more and fixed typo.

{\color{red} When two loop corrections have been enabled in the SLHA
  file by setting entry 4 of the FlexibleSUSY block to 2 the user may
  also select individual corrections. Entries 9,10,11 and 12,
  corrspond to two loop corrections of order $\oatas$, $\oabas$,
  $\oatplusabsq$ and $\oatauq$ respectively and will be disabled when
  the corresponding entry is set to zero. In this way, for example, in
  the NMSSM the user may decide not to use the partial corrections at
  order $\oatplusabsq$ and $\oatauq$, all of which have
  only been computed in the MSSM. }

Since the Higgs mass is a very important measurement and
the two-loop corrections can be larger than the current experimental
error \cite{Degrassi:2009yq} we recommend to set these switches to
\code{True} in any MSSM-\footnote{In \fs a model is MSSM-like if (i)
  its superpotential is approximately given by the MSSM one, (ii) it
  implements $R$-parity conservation or something equivalent, and
  (iii) contains two CP-even and CP-odd Higgs bosons, where one CP-odd
  Higgs boson may be a Goldstone boson, all with an MSSM-like coupling
  to $t$, $b$ and $\tau$.} and NMSSM-like\footnote{In \fs a model is
  NMSSM-like if (i) its superpotential is approximately given by the
  NMSSM one, (ii) it implements $R$-parity conservation or something
  equivalent, and (iii) contains three CP-even and CP-odd Higgs
  bosons, where one or two CP-odd Higgs bosons may be Goldstone
  bosons, all with an NMSSM-like coupling to $t$, $b$ and $\tau$\@.
  Examples for NMSSM-like models are the USSM and the \ESSM.} model.
However in such models the user should still consider whether these
corrections are really the leading corrections in the model or if
there are other potentially large two-loop corrections.  For models
with a more extended Higgs sector we recommend that the leading log
two-loop corrections are estimated by generalizing those of the MSSM
or NMSSM.

>>>>

  When two loop corrections have been enabled in the SLHA
  file by setting entry 4 of the FlexibleSUSY block to 2 the user may
  also select individual corrections. Entries 9,10,11 and 12,
  correspond to two loop corrections of order $\oatas$, $\oabas$,
  $\oatplusabsq$ and $\oatauq$ respectively and will be disabled when
  the corresponding entry is set to zero. In this way, for example, in
  the NMSSM the user may decide not to use the partial corrections at
  order $\oatplusabsq$ and $\oatauq$, all of which have
  only been computed in the MSSM.

Since the Higgs mass is a very important measurement and the two-loop
corrections can be larger than the current experimental error
\cite{Degrassi:2009yq} we recommend to set these switches to
\code{True} in any MSSM-\footnote{In \fs a model is MSSM-like if (i)
  its superpotential is approximately given by the MSSM one, (ii) it
  implements $R$-parity conservation or something equivalent, and
  (iii) contains two CP-even and CP-odd Higgs bosons, where one CP-odd
  Higgs boson may be a Goldstone boson, all with an MSSM-like coupling
  to $t$, $b$ and $\tau$.} and NMSSM-like\footnote{In \fs a model is
  NMSSM-like if (i) its superpotential is approximately given by the
  NMSSM one, (ii) it implements $R$-parity conservation or something
  equivalent, and (iii) contains three CP-even and CP-odd Higgs
  bosons, where one or two CP-odd Higgs bosons may be Goldstone
  bosons, all with an NMSSM-like coupling to $t$, $b$ and $\tau$\@.
  Examples for NMSSM-like models are the USSM and the \ESSM.} model.
However in such models the user should still consider whether these
corrections are really the leading corrections in the model or if
there are other potentially large two-loop corrections which are
missing.  For models with a more extended Higgs sector we recommend
that the leading log two-loop corrections are estimated by
generalizing those of the MSSM or NMSSM.
